disaggregation: An \proglang{R} Package for Bayesian Spatial Disaggregation Modelling

### 2020-02-07 article.Rnw
Add other implementations.

The popular R package \pkg{INLA} can perform disaggregation regression in the simplest case of ...

li etc.

>>>>

A number of other implementations use statistical models to estimate high resolution disease risk from aggregated disease data.
To the best of our knowledge, these all only include covariates at the polygon level rather than at the pixel level.
The popular R package \pkg{INLA} can perform disaggregation regression in the simplest case of a normal likelihood, an identity link function and no high resolution covariates \citep{moraga2017geostatistical, INLA, wilson2017pointless}. 
The \pkg{SDALGCP} package fits the model using Monte Carlo Maximum Likelihood \citep{johnson2019spatially}.
It can only fit models with a Poisson likelihood with covariates at the polygon level.
Finally, the \pkg{lgcp} package uses a data augmentation approach to fit models to aggregated data \citep{lgcp}.  
This Monte Carlo data augmentation approach will be very slow for large areas or large numbers of cases.
